### 2007-10-16 pkg/paper/article.Rnw
added a little more on gamma correction
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@10 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Gamma correction}

@@

>>>>

\subsection{Gamma correction}

The RGB tristimulus values that we have calculated to this point 
have taken into account the SPDs of the red, green, and blue 
pixels on a screen (the primaries), 
and the relative powerfulness of each channel 
(the white point), but we still have to worry about the non-linear
relationship between the input values and the amount of light
emitted from each pixel (the display gamma).

We know that RGB tristimulus values will undergo an exponential 
transformation when displayed by the monitor, so we invert that
transformation in the tristimulus values that we store.

The exponential transformation may vary between different screens
or projectors, but again there is a standard transformation 
that is implemented in most modern equipment.

$$C' = \left\{\begin{array}{l l}12.92C & \quad C \leq 0.0031308 \\
                                (1 + \alpha)C^{1/2.4} - 0.055 & 
                                \quad C > 0.0031308 \\
             \end{array} 
      \right.$$

@@

HLS (and others) because you may have been given a colour in
such a (crappy) colorspace and want to convert it to something
better in order to work with it.
